---
title: "W_UP_01"
author: "Hannah Vong"
date: "fall 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

The question is there a difference between the average number of pushups that can be done in two minutes between skilled and line players.
The data came from George Town College in Kentucky.


Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

Pushups is an numerical variable, position is categorical therefore we use numerical-cat file.

# Results

```{r}
boxplot(pushups~position,data=mydata)
```
<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->
This box-plot shows that the skill player do more push-ups in 2 minutes on average than line players.

### Numerical Descriptive Results

```{r}
favstats(pushups~position,data=mydata)
```
This table shows that the average number of push - ups for a line player was 17, while the average for a skill player was 50 

## Inferential Results

```{r}
t.test(momheight~Sex,data=ucdavis1)
```

P value is less than 0.05 so we reject the null hypothesis and conclude there is a difference betwween the amount of push- ups  a line player and skill player can do in 2 minutes



```
  
  
<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->


<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->


## Discussion and Conclusion
The original question  was is there a difference in the average numbers of push-ups  that the line player can do against a skill player in 2 minutes , There is difference between whether or not the players can do more push-ups than each other in 2 minutes . In fact , skill player can do more push-ups . Line players can do an average of 17 push - ups in 2 minutes. While on the other hand, skill players can do an average of 50 push -ups in 2 minutes.

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
The original question was is there a difference in the average number of pushups that skill and line players can do in 2 minutes.

The original


